Work Stress

### 2023-03-17 outputs/paper/paper.qmd
Update paper to include minor changes on each figure's axis titles

clean_data %>% 
  ggplot(aes(group = wrkstat)) +
  geom_bar(aes(x=stress, y = ..prop.., fill=factor(..x..)))+
  labs(y = "Percent", fill="Work Stress", x = 'Work Stress', title = "Work Stress by status" ) +
  facet_wrap(~wrkstat) +
  scale_x_discrete(limits = positions) +
  scale_y_continuous(labels = scales::percent) +
  theme_minimal(base_size = 8) +
  theme(legend.position="none")
```

@@

clean_data %>% 
  ggplot() +
  geom_bar(aes(x = stress,  y = ..prop.., group = range, fill=factor(..x..))) +
  scale_x_discrete(limits = positions) +
  scale_y_continuous(labels = scales::percent) +
  facet_wrap(~range) +
  theme_minimal(base_size = 6) +
  theme(legend.position="none")
```

@@

clean_data %>% 
  ggplot() +
  geom_bar(aes(x = stress,  y = ..prop.., group = wrkgovt, fill=factor(..x..))) +
  scale_x_discrete(limits = positions) +
  scale_y_continuous(labels = scales::percent) +
  facet_wrap(~wrkgovt) +
  theme_minimal(base_size = 8) +
  theme(legend.position="none")
```

@@

clean_data %>% 
  ggplot() +
  geom_bar(aes(x = stress,  y = ..prop.., group = satjob, fill=factor(..x..))) +
  scale_x_discrete(limits = positions) +
  scale_y_continuous(labels = scales::percent) +
  facet_wrap(~satjob) +
  theme_minimal(base_size = 6) +
  theme(legend.position="none")
```

>>>>

clean_data %>% 
  ggplot(aes(group = wrkstat)) +
  geom_bar(aes(x=stress, y = ..prop.., fill=factor(..x..)))+
  labs(y = "Percentage", fill="Work Stress", x = 'Work Stress', title = "Work Stress by Status" ) +
  facet_wrap(~wrkstat) +
  scale_x_discrete(limits = positions) +
  scale_y_continuous(labels = scales::percent) +
  theme_minimal(base_size = 8) +
  theme(legend.position="none")
```

@@

clean_data %>% 
  ggplot() +
  geom_bar(aes(x = stress,  y = ..prop.., group = range, fill=factor(..x..))) +
  labs(y = "Percentage", fill="Work Stress", x = 'Work Stress', title = "Work Stress by Work Hours" ) +
  scale_x_discrete(limits = positions) +
  scale_y_continuous(labels = scales::percent) +
  facet_wrap(~range) +
  theme_minimal(base_size = 6) +
  theme(legend.position="none")
```

@@

clean_data %>% 
  ggplot() +
  geom_bar(aes(x = stress,  y = ..prop.., group = wrkgovt, fill=factor(..x..))) +
  labs(y = "Percentage", fill=" Work Stress", x = 'Work Stress', title = "Work Stress by Industry Sector" ) +
  scale_x_discrete(limits = positions) +
  scale_y_continuous(labels = scales::percent) +
  facet_wrap(~wrkgovt) +
  theme_minimal(base_size = 8) +
  theme(legend.position="none")
```

@@

clean_data %>% 
  ggplot() +
  geom_bar(aes(x = stress,  y = ..prop.., group = satjob, fill=factor(..x..))) +
  labs(y = "Percentage", fill="Work Stress", x = 'Work Stress', title = "Work Stress by Job Satisfaction" ) +
  scale_x_discrete(limits = positions) +
  scale_y_continuous(labels = scales::percent) +
  facet_wrap(~satjob) +
  theme_minimal(base_size = 6) +
  theme(legend.position="none")
```
